### 2016-12-08 local-capability-machine.tex
push with pwl lemma, awkward example work in progress

%Math notation
\newcommand{\restrictfun}[1]{|_{#1}}
\newcommand{\parfun}{\rightharpoonup}
\newcommand{\finparfun}{\xrightharpoonup{\textit{\tiny{fin}}}}
\newcommand{\monnefun}{\xrightarrow{\textit{\tiny{mon, ne}}}}
\newcommand{\monfun}{\xrightarrow{\textit{\tiny{mon}}}}
\newcommand{\nefun}{\xrightarrow{\textit{\tiny{ne}}}}
\newcommand{\fun}{\rightarrow}
\newcommand{\defeq}{\stackrel{\textit{\tiny{def}}}{=}}
\newcommand{\nequal}[1][n]{\stackrel{\tiny{#1}}{=}}
\renewcommand{\nsim}[1][n]{\stackrel{\tiny{#1}}{\simeq}}

@@

%cofes
\newcommand{\cofe}{c.o.f.e.}
\newcommand{\cofes}{\cofe{}'s}
\newcommand{\CatC}{\mathbb{C}}
\newcommand{\CatP}{\mathbb{P}}

%Comments
\newcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\newcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\newcommand\lars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

%Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}
\newcommand{\olf}{\var{offsetLinkFlag}}
\newcommand{\prp}{\var{prp}}

%Memory projections
\newcommand{\plainproj}[1]{\mathrm{#1}}
\newcommand{\memheap}[1][\Phi]{#1.\plainproj{mem}}
\newcommand{\memreg}[1][\Phi]{#1.\plainproj{reg}}

@@

%Configuration end states
\newcommand{\failed}{\textsl{failed}}
\newcommand{\halted}{\textsl{halted}}

%Functions
\newcommand{\plainfun}[2]{
  \ifthenelse{\equal{#2}{}}
             {\mathit{#1}}
             {\mathit{#1}(#2)}
}
\newcommand{\decode}{\plainfun{decode}{}}
\newcommand{\encode}{\plainfun{encode}{}}
\newcommand{\encodePerm}{\mathit{encodePerm}}
\newcommand{\encodePermPair}{\plainfun{encodePermPair}{}}
\newcommand{\encodeLoc}{\mathit{encodeLoc}{}}
\newcommand{\decodePermPair}{\plainfun{decodePermPair}}
\newcommand{\decodePerm}[1]{\plainfun{decodePerm}{#1}}
\newcommand{\updatePcPerm}[1]{\plainfun{updatePcPerm}{#1}}

@@

%World operations
\newcommand{\future}{\mathbin{\sqsupseteq}}
\newcommand{\futurewk}{\mathbin{\sqsupseteq}^{\var{pub}}}
\newcommand{\futurestr}{\mathbin{\sqsupseteq}^{\var{priv}}}
\newcommand{\heapSat}[3][\heap]{#1 :_{#2} #3}
\newcommand{\memSat}[3][n]{\heapSat[#2]{#1}{#3}}
\newcommand{\memSatPar}[4][n]{\heapSat[#2]{#1 , #4}{#3}}

@@

%Assembly labels
\newcommand{\codelabel}[1]{\mathit{#1}}
\newcommand{\init}{\codelabel{init}}
\newcommand{\malloc}{\codelabel{malloc}}
\newcommand{\counter}{\codelabel{counter}}
\newcommand{\iocap}{\codelabel{iocap}}

%Type(s)
\newcommand{\type}[1]{\mathrm{#1}}
\newcommand{\asmType}{\plaindom{AsmType}}

%Domains
\newcommand{\plaindom}[1]{\mathrm{#1}}
\newcommand{\Caps}{\plaindom{Cap}}
\newcommand{\Words}{\plaindom{Word}}
\newcommand{\Addrs}{\plaindom{Addr}}
\newcommand{\ExecConfs}{\plaindom{ExecConf}}
\newcommand{\RegName}{\plaindom{RegisterName}}
\newcommand{\Regs}{\plaindom{Reg}}
\newcommand{\Heaps}{\plaindom{Mem}}
\newcommand{\Mems}{\Heaps}
\newcommand{\HeapSegments}{\plaindom{MemSegment}}
\newcommand{\MemSegments}{\HeapSegments}
\newcommand{\Confs}{\plaindom{Conf}}
\newcommand{\Instrs}{\plaindom{Instructions}}
\newcommand{\nats}{\mathbb{N}}
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\Perms}{\plaindom{Perm}}
\newcommand{\Globals}{\plaindom{Global}}

@@

%LR
\newcommand{\intr}[2]{\mathcal{#1}}
\newcommand{\valueintr}[1]{\intr{V}{#1}}
\newcommand{\exprintr}[1]{\intr{E}{#1}}
\newcommand{\contintr}[1]{\intr{K}{#1}}
\newcommand{\regintr}[1]{\intr{R}{#1}}
\newcommand{\stdvr}{\valueintr{\asmType}}
\newcommand{\stder}{\exprintr{\asmType}}
\newcommand{\stdrr}{\regintr{\asmType}}
\newcommand{\stdkr}{\contintr{\asmType}}
\newcommand{\observations}{\mathcal{O}}
\newcommand{\npair}[2][n]{\left(#1,#2 \right)}

%Reference register/memory
\newcommand{\refreg}[1]{\lfloor #1 \rfloor}
\newcommand{\refheap}[1]{\langle #1 \rangle_m}

%Instructions
%No arguments
\newcommand{\zinstr}[1]{\mathtt{#1}}
\newcommand{\fail}{\zinstr{fail}}
\newcommand{\halt}{\zinstr{halt}}
%One argument
\newcommand{\oneinstr}[2]{\zinstr{#1} \; #2}
\newcommand{\jmp}[1]{\oneinstr{jmp}{#1}}
%Two arguments
\newcommand{\twoinstr}[3]{\zinstr{#1} \; #2 \; #3}
\newcommand{\restricttwo}[2]{\twoinstr{restrict}{#1}{#2}}
\newcommand{\jnz}[2]{\twoinstr{jnz}{#1}{#2}}
\newcommand{\isptr}[2]{\twoinstr{isptr}{#1}{#2}}
\newcommand{\geta}[2]{\twoinstr{geta}{#1}{#2}}
\newcommand{\getb}[2]{\twoinstr{getb}{#1}{#2}}
\newcommand{\gete}[2]{\twoinstr{gete}{#1}{#2}}
\newcommand{\getp}[2]{\twoinstr{getp}{#1}{#2}}
\newcommand{\getl}[2]{\twoinstr{getl}{#1}{#2}}
\newcommand{\move}[2]{\twoinstr{move}{#1}{#2}}
\newcommand{\store}[2]{\twoinstr{store}{#1}{#2}}
\newcommand{\load}[2]{\twoinstr{load}{#1}{#2}}
\newcommand{\lea}[2]{\twoinstr{lea}{#1}{#2}}
%Three arguments
\newcommand{\threeinstr}[4]{\zinstr{#1} \; #2 \; #3 \; #4}
\newcommand{\restrict}[3]{\threeinstr{restrict}{#1}{#2}{#3}}
\newcommand{\subseg}[3]{\threeinstr{subseg}{#1}{#2}{#3}}
\newcommand{\plus}[3]{\threeinstr{plus}{#1}{#2}{#3}}

%Permissions
\newcommand{\plainperm}[1]{\mathrm{#1}}
\newcommand{\noperm}{\plainperm{o}}
\newcommand{\readonly}{\plainperm{ro}}
\newcommand{\readwrite}{\plainperm{rw}}
\newcommand{\exec}{\plainperm{rx}}
\newcommand{\entry}{\plainperm{e}}
\newcommand{\rwx}{\plainperm{rwx}}
%PWL permissions
\newcommand{\readwritel}{\plainperm{rwl}}
\newcommand{\rwlx}{\plainperm{rwlx}}

%Global/local
\newcommand{\local}{\plainperm{local}}
\newcommand{\glob}{\plainperm{global}}

@@

%Views
\newcommand{\plainview}[1]{\mathrm{#1}}
\newcommand{\perma}{\plainview{perm}}
\newcommand{\temp}{\plainview{temp}}
\newcommand{\revoked}{\plainview{revoked}}

%OP sem
\newcommand{\diverge}[1][n]{\not\Downarrow_{#1}}
\newcommand{\step}[1][]{\rightarrow_{#1}}

@@

%TODO: \Phi.reg(rv) to some other notation. It should only look up reg, if it is a regname otherwise just the litteral.

@@

\begin{lemma}[Correctness lemma for \texttt{f2}]
  \label{lem:correctness-f2}
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\olf,\mathtt{2f},\mathtt{f2}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\olf,\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \qquad \text{ for all $n \in \nats$}
  \end{align*}
  and
  \begin{itemize}
  \item $\ms_{f2}(\mathtt{f2}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f2}(\mathtt{f2}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [\flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}

@@

      %TODO - this should be similar to previous proofs

@@

            %TODO - typeout the details. 

@@

                    \update{i_3}{\iota_x}

@@

            \iota_x & = (\perm,0,\{(0,1),(0,0),(1,1)\},\{(1,0),(0,1),(0,0),(1,1)\},H_x) \\

@@

          %TODO insert tikz picture of machine (just like Dreyer Neis machine.)

@@

          SFTS:
          \begin{enumproof}
            \item$\memSat[n^{(3)}]{\ms''}$
              %TODO should be simple - all existing regions have interpretations monotone wrt public future worlds. The malloc island uses its "isolation condition" which makes room for the two new islands. The x islands starts in state 0 (and the appropriate memory address contains 0). The env and cls islands are static islands designed to accept exactly what the memory contains.
            \item $\npair[n^{(3)}]{\reg''} \in \stdrr(W'')$ amounts to showing:
              \begin{enumproof}
                \item For $r \in \RegName \setminus \{\pcreg, r_0, r_1 \}$ $\reg''(r) = 0$ and it is trivial to show $\npair[n^{(3)}]{0} \in \stdvr(W'')$. 
                \item $\npair[n^{(3)}]{\reg'(r_0)} \in \stdvr(W'')$ - follows from \ref{g1:regrel1} and public monotonicity of $\stdvr$.
                \item $\npair[n^{(3)}]{((\entry,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)} \in \stdvr(W'')$ \\
                  To this end let $n^{(4)} < n^{(3)}$, $W^{(3)} \futurestr W''$ be given and assume
                  \begin{align*}
                    \\ \npair[n^{(4)}]{\reg^{(3)}} \in \stdrr(W^{(3)}) &
                    \\ \memSat[n^{(4)}]{\ms^{(3)}}{W^{(3)}} \label{g1:memsat-cls}
                  \end{align*}
                  for some $\reg^{(3)}$ and $\ms^{(3)}$ and show
                  \[
                    \npair[n^{(4)}]{(\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)})} \in \observations(W^{(3)})
                  \]
                  to this end let $j \leq n^{(4)}$, $m^{(3)}$, and $m_f'$ be given and assume
                  \begin{equation}
                    (\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)} \uplus \ms_f') \step[j] (\halted, m^{(3)}) \label{g1:execution2}
                  \end{equation}
                  and show
                  \begin{equation}
                    \exists W_{\var{str}}^{(3)} \futurestr W^{(3)}, \ms'^{(3)}, \ms_r \ldotp m^{(3)} = \ms'^{(3)} \uplus \ms_r \uplus \ms_f' \land \memSat[n^{(4)}-j]{\ms'^{(3)}}{W_{\var{str}}'} \label{g1:g-goal2}
                  \end{equation}
                  to this end consider what happens in execution \ref{g1:execution2}: Due to \label{g1:memsat-cls} we know that the activation code and $f4$ code is unaltered. Running the activation code loads the environment capability to $r_{\var{env}}$ and loads the $f4$ capability, then the $r_1$ register is tested whether it contains a global capability and the $r_\stk$ register is tested for whether it contains an $\rwlx$ capability, say $\reg''(r_\stk) = ((\rwlx, \gl), \start_{\stk}', \addrend_{\stk}', \addr_{\stk}')$. As we know the execution halts succesfully, both of these checks must succeed.

>>>>

% Math notation
\newcommand{\restrictfun}[1]{|_{#1}}
\newcommand{\parfun}{\rightharpoonup}
\newcommand{\finparfun}{\xrightharpoonup{\textit{\tiny{fin}}}}
\newcommand{\monnefun}{\xrightarrow{\textit{\tiny{mon, ne}}}}
\newcommand{\monfun}{\xrightarrow{\textit{\tiny{mon}}}}
\newcommand{\nefun}{\xrightarrow{\textit{\tiny{ne}}}}
\newcommand{\fun}{\rightarrow}
\newcommand{\defeq}{\stackrel{\textit{\tiny{def}}}{=}}
\newcommand{\nequal}[1][n]{\stackrel{\tiny{#1}}{=}}
\renewcommand{\nsim}[1][n]{\stackrel{\tiny{#1}}{\simeq}}

@@

% cofes
\newcommand{\cofe}{c.o.f.e.}
\newcommand{\cofes}{\cofe{}'s}
\newcommand{\CatC}{\mathbb{C}}
\newcommand{\CatP}{\mathbb{P}}

% Comments
\newcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\newcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\newcommand\lars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

% Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}
\newcommand{\olf}{\var{offsetLinkFlag}}
\newcommand{\prp}{\var{prp}}

% Memory projections
\newcommand{\plainproj}[1]{\mathrm{#1}}
\newcommand{\memheap}[1][\Phi]{#1.\plainproj{mem}}
\newcommand{\memreg}[1][\Phi]{#1.\plainproj{reg}}

@@

% Configuration end states
\newcommand{\failed}{\textsl{failed}}
\newcommand{\halted}{\textsl{halted}}

% Functions
\newcommand{\plainfun}[2]{
  \ifthenelse{\equal{#2}{}}
  {\mathit{#1}}
  {\mathit{#1}(#2)}
}
\newcommand{\decode}{\plainfun{decode}{}}
\newcommand{\encode}{\plainfun{encode}{}}
\newcommand{\encodePerm}{\mathit{encodePerm}}
\newcommand{\encodePermPair}{\plainfun{encodePermPair}{}}
\newcommand{\encodeLoc}{\mathit{encodeLoc}{}}
\newcommand{\decodePermPair}{\plainfun{decodePermPair}}
\newcommand{\decodePerm}[1]{\plainfun{decodePerm}{#1}}
\newcommand{\updatePcPerm}[1]{\plainfun{updatePcPerm}{#1}}

@@

% World operations
\newcommand{\future}{\mathbin{\sqsupseteq}}
\newcommand{\futurewk}{\mathbin{\sqsupseteq}^{\var{pub}}}
\newcommand{\futurestr}{\mathbin{\sqsupseteq}^{\var{priv}}}
\newcommand{\heapSat}[3][\heap]{#1 :_{#2} #3}
\newcommand{\memSat}[3][n]{\heapSat[#2]{#1}{#3}}
\newcommand{\memSatPar}[4][n]{\heapSat[#2]{#1 , #4}{#3}}

@@

% Assembly labels
\newcommand{\codelabel}[1]{\mathit{#1}}
\newcommand{\init}{\codelabel{init}}
\newcommand{\malloc}{\codelabel{malloc}}
\newcommand{\counter}{\codelabel{counter}}
\newcommand{\iocap}{\codelabel{iocap}}

% Type(s)
\newcommand{\type}[1]{\mathrm{#1}}
\newcommand{\asmType}{\plaindom{AsmType}}

% Domains
\newcommand{\plaindom}[1]{\mathrm{#1}}
\newcommand{\Caps}{\plaindom{Cap}}
\newcommand{\Words}{\plaindom{Word}}
\newcommand{\Addrs}{\plaindom{Addr}}
\newcommand{\ExecConfs}{\plaindom{ExecConf}}
\newcommand{\RegName}{\plaindom{RegisterName}}
\newcommand{\Regs}{\plaindom{Reg}}
\newcommand{\Heaps}{\plaindom{Mem}}
\newcommand{\Mems}{\Heaps}
\newcommand{\HeapSegments}{\plaindom{MemSegment}}
\newcommand{\MemSegments}{\HeapSegments}
\newcommand{\Confs}{\plaindom{Conf}}
\newcommand{\Instrs}{\plaindom{Instructions}}
\newcommand{\nats}{\mathbb{N}}
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\Perms}{\plaindom{Perm}}
\newcommand{\Globals}{\plaindom{Global}}

@@

% LR
\newcommand{\intr}[2]{\mathcal{#1}}
\newcommand{\valueintr}[1]{\intr{V}{#1}}
\newcommand{\exprintr}[1]{\intr{E}{#1}}
\newcommand{\contintr}[1]{\intr{K}{#1}}
\newcommand{\regintr}[1]{\intr{R}{#1}}
\newcommand{\stdvr}{\valueintr{\asmType}}
\newcommand{\stder}{\exprintr{\asmType}}
\newcommand{\stdrr}{\regintr{\asmType}}
\newcommand{\stdkr}{\contintr{\asmType}}
\newcommand{\observations}{\mathcal{O}}
\newcommand{\npair}[2][n]{\left(#1,#2 \right)}

% Reference register/memory
\newcommand{\refreg}[1]{\lfloor #1 \rfloor}
\newcommand{\refheap}[1]{\langle #1 \rangle_m}

% Instructions
% No arguments
\newcommand{\zinstr}[1]{\mathtt{#1}}
\newcommand{\fail}{\zinstr{fail}}
\newcommand{\halt}{\zinstr{halt}}
% One argument
\newcommand{\oneinstr}[2]{\zinstr{#1} \; #2}
\newcommand{\jmp}[1]{\oneinstr{jmp}{#1}}
% Two arguments
\newcommand{\twoinstr}[3]{\zinstr{#1} \; #2 \; #3}
\newcommand{\restricttwo}[2]{\twoinstr{restrict}{#1}{#2}}
\newcommand{\jnz}[2]{\twoinstr{jnz}{#1}{#2}}
\newcommand{\isptr}[2]{\twoinstr{isptr}{#1}{#2}}
\newcommand{\geta}[2]{\twoinstr{geta}{#1}{#2}}
\newcommand{\getb}[2]{\twoinstr{getb}{#1}{#2}}
\newcommand{\gete}[2]{\twoinstr{gete}{#1}{#2}}
\newcommand{\getp}[2]{\twoinstr{getp}{#1}{#2}}
\newcommand{\getl}[2]{\twoinstr{getl}{#1}{#2}}
\newcommand{\move}[2]{\twoinstr{move}{#1}{#2}}
\newcommand{\store}[2]{\twoinstr{store}{#1}{#2}}
\newcommand{\load}[2]{\twoinstr{load}{#1}{#2}}
\newcommand{\lea}[2]{\twoinstr{lea}{#1}{#2}}
% Three arguments
\newcommand{\threeinstr}[4]{\zinstr{#1} \; #2 \; #3 \; #4}
\newcommand{\restrict}[3]{\threeinstr{restrict}{#1}{#2}{#3}}
\newcommand{\subseg}[3]{\threeinstr{subseg}{#1}{#2}{#3}}
\newcommand{\plus}[3]{\threeinstr{plus}{#1}{#2}{#3}}

% Permissions
\newcommand{\plainperm}[1]{\mathrm{#1}}
\newcommand{\noperm}{\plainperm{o}}
\newcommand{\readonly}{\plainperm{ro}}
\newcommand{\readwrite}{\plainperm{rw}}
\newcommand{\exec}{\plainperm{rx}}
\newcommand{\entry}{\plainperm{e}}
\newcommand{\rwx}{\plainperm{rwx}}
% PWL permissions
\newcommand{\readwritel}{\plainperm{rwl}}
\newcommand{\rwlx}{\plainperm{rwlx}}

% Global/local
\newcommand{\local}{\plainperm{local}}
\newcommand{\glob}{\plainperm{global}}

@@

% Views
\newcommand{\plainview}[1]{\mathrm{#1}}
\newcommand{\perma}{\plainview{perm}}
\newcommand{\temp}{\plainview{temp}}
\newcommand{\revoked}{\plainview{revoked}}

% OP sem
\newcommand{\diverge}[1][n]{\not\Downarrow_{#1}}
\newcommand{\step}[1][]{\rightarrow_{#1}}

@@

% TODO: \Phi.reg(rv) to some other notation. It should only look up reg, if it is a regname otherwise just the litteral.

@@

              \begin{lemma}[Correctness lemma for \texttt{f2}]
                \label{lem:correctness-f2}
                  c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\olf,\mathtt{2f},\mathtt{f2}) \\
                  c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
                  \reg & \in \Regs \\
                  m & \defeq \hs_{f2} \uplus 
                      \ms_{\malloc} \uplus 
                      \ms_{\var{stk}} \uplus
                  &\dom(\hs_{f2}) = [\mathtt{f2}-\olf,\mathtt{2f}] \\
                  &\dom(\ms_\link) = [\link,\link+1]\\
                  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \qquad \text{ for all $n \in \nats$}
                \item $\ms_{f2}(\mathtt{f2}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f2}(\mathtt{f2}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f2}$ contains the code of $f2$.
                \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
                \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
                  (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
              \begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
                Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
                \begin{multline*}
                  (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
                  (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
                \end{multline*}
                Where 
                  m''  \defeq \hs_{f2} \uplus 
                  \ms_\stk' \uplus
                Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
                \item The range of authority for 
                  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
                  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
                  the two stack capabilities have the same permissions as $c_\stk$
                \item $c_{f2}'$ points to the return address in f2's code.
                \item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
                \item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.

@@

                  % TODO - this should be similar to previous proofs

@@

                      % TODO - typeout the details. 

@@

                      \update{i_3}{\iota_{x,0}}

@@

                      \iota_{x,s} & = (\perm,s,\{(0,1),(0,0),(1,1)\},\{(1,0),(0,1),(0,0),(1,1)\},H_x) \\

@@

                    % TODO insert tikz picture of machine (just like Dreyer Neis machine.) and prove that it is indeed a region (should be simple, interpretation does not depend on world).

@@

                    SFTS:
                    \begin{enumproof}
                    \item$\memSat[n^{(3)}]{\ms''}$
                      % TODO should be simple - all existing regions have interpretations monotone wrt public future worlds. The malloc island uses its "isolation condition" which makes room for the two new islands. The x islands starts in state 0 (and the appropriate memory address contains 0). The env and cls islands are static islands designed to accept exactly what the memory contains.
                    \item $\npair[n^{(3)}]{\reg''} \in \stdrr(W'')$ amounts to showing:
                      \begin{enumproof}
                      \item For $r \in \RegName \setminus \{\pcreg, r_0, r_1 \}$ $\reg''(r) = 0$ and it is trivial to show $\npair[n^{(3)}]{0} \in \stdvr(W'')$. 
                      \item $\npair[n^{(3)}]{\reg'(r_0)} \in \stdvr(W'')$ - follows from \ref{g1:regrel1} and public monotonicity of $\stdvr$.
                      \item $\npair[n^{(3)}]{((\entry,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)} \in \stdvr(W'')$ \\
                        To this end let $n^{(4)} < n^{(3)}$, $W^{(3)} \futurestr W''$ be given and assume
                        \begin{align}
                          \\ \npair[n^{(4)}]{\reg^{(3)}} \in \stdrr(W^{(3)}) \label{g1:reg-file-cls} &
                          \\ \memSat[n^{(4)}]{\ms^{(3)}}{W^{(3)}} \label{g1:memsat-cls}
                        \end{align}
                        for some $\reg^{(3)}$ and $\ms^{(3)}$ and show
                        \[
                          \npair[n^{(4)}]{(\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)})} \in \observations(W^{(3)})
                        \]
                        to this end let $j \leq n^{(4)}$, $m^{(3)}$, and $m_f'$ be given and assume
                        \begin{equation}
                          (\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)} \uplus \ms_f') \step[j] (\halted, m^{(3)}) \label{g1:execution2}
                        \end{equation}
                        and show
                        \begin{equation}
                          \exists W_{\var{str}}^{(3)} \futurestr W^{(3)}, \ms'^{(3)}, \ms_r \ldotp m^{(3)} = \ms'^{(3)} \uplus \ms_r \uplus \ms_f' \land \memSat[n^{(4)}-j]{\ms'^{(3)}}{W_{\var{str}}'} \label{g1:g-goal2}
                        \end{equation}
                        to this end consider what happens in execution \ref{g1:execution2}: Due to \label{g1:memsat-cls} we know that the activation code and $f4$ code is unaltered. Running the activation code loads the environment capability to $r_{\var{env}}$ and loads the $f4$ capability, then the $r_1$ register is tested whether it contains a global capability (which it does s execution does not fail) and the $r_\stk$ register is tested for whether it contains an $\rwlx$ capability (which it does as execution does not fail), and the pointer address is adjusted, so the $r_\stk$-register now contains $((\rwlx, \gl), \start_{\stk}', \addrend_{\stk}', \start_{\stk}'-1)$.
